### 2020-07-01 testing/docs/LaTex/Paper.tex
Adds docs to testing folder to make a second version

\subsubsection{Simple Graphical Interface}
Despite FIWARE is a powerful platform, is not friendly enough regarding to final user. This is why a the end of this document is described a simple graphical interface developed to manage end-nodes in FIWARE side. As will be indicated, this graphical interface has been developed using python and its tkinter module intended to build graphical interfaces.

@@

Regarding to LoRaWAN and TTN security, as previously indicated, the chosen method is ABP, so are necessary the \cmd{NWKSKEY} (Network Session Key), \cmd{APPSKEY} (Application Session Key) and \cmd{DEVADDR} (End-Device Address); these constants placed at lines \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L48}{48}, \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L52}{52} and \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L57}{57} must be obtained from TTN console as will be explained in \hyperref[sssec:TTN_Stack]{The Things Network Stack} subsection, so \textbf{pleas, refer to that subsection for further details}. The sketch also sets analog pin \cmd{A2} to acquire the sensor signal as can be seen in line \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L70}{70}.% as well as the payload to send through LoRa interface in line \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L65}{65}

@@

\subsubsection{The Things Network Stack}\label{sssec:TTN_Stack}
This is a platform for the LoRaWAN protocol where is possible to manage gateways, devices and applications. It provides a centralized way to manage these kind of things regard in security too, generating several keys to tight the end-devices to the chosen server cloud solution (FIWARE in this case). There are three fundamental process the reader must follow to include nodes and gateways in the platform, those are luckily pretty well documented.

@@

Once these steps are completed, the TTN web interface will provide an overview with all data regarding to the device like figure \ref{fig:dev_overview} shows.

@@

To check Orion Context Broker, IoTagent-LoRaWAN and QuantumLeap versions running in the docker containers the reader has to click on \enquote{About} tab, however, this first shown tab ---\enquote{Application Keys}--- is the most important one because without complete all the required info won't be enabled the \enquote{Devices Management} tab. Actually this tab performs a series of checks regard in TTN keys. Following the same TTN requirements,

>>>>

\subsubsection{Simple Graphical Interface}
Despite FIWARE is a powerful platform, is not friendly enough regarding final user. This is why a the end of this document is described a simple graphical interface developed to manage end-nodes in FIWARE side. As will be indicated, this graphical interface has been developed using python and its tkinter module intended to build graphical interfaces.

@@

With regards to LoRaWAN and TTN security, as previously indicated, the chosen method is ABP, so are necessary the \cmd{NWKSKEY} (Network Session Key), \cmd{APPSKEY} (Application Session Key) and \cmd{DEVADDR} (End-Device Address); these constants placed at lines \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L48}{48}, \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L52}{52} and \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L57}{57} must be obtained from TTN console as will be explained in \hyperref[sssec:TTN_Stack]{The Things Network Stack} subsection, so \textbf{pleas, refer to that subsection for further details}. The sketch also sets analog pin \cmd{A2} to acquire the sensor signal as can be seen in line \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L70}{70}.% as well as the payload to send through LoRa interface in line \href{https://github.com/WyRe/lora-arduino-dendrometer/blob/master/src/arduino/dendro/dendro.ino#L65}{65}

@@

\subsubsection{The Things Network Stack}\label{sssec:TTN_Stack}
This is a platform for the LoRaWAN protocol where is possible to manage gateways, devices and applications. It provides a centralized way to manage these kind of things regarding security too, generating several keys to tight the end-devices to the chosen server cloud solution (FIWARE in this case). There are three fundamental process the reader must follow to include nodes and gateways in the platform, those are luckily pretty well documented.

@@

Once these steps are completed, the TTN web interface will provide an overview with all data regarding the device like figure \ref{fig:dev_overview} shows.

@@

To check Orion Context Broker, IoTagent-LoRaWAN and QuantumLeap versions running in the docker containers the reader has to click on \enquote{About} tab, however, this first shown tab ---\enquote{Application Keys}--- is the most important one because without complete all the required info won't be enabled the \enquote{Devices Management} tab. Actually this tab performs a series of checks regarding TTN keys. Following the same TTN requirements,
